Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-01-18 paper/main.tex
adjust text of individual results

% intro
Third, we investigated result from both naturalistic paradigms on the level of
individual subjects.
%
Focussing on the AD stimulus, wee hypothesize[d] that an exclusively auditory
stimulus can/could localize ``visual area'' in individual subjects and thus
possibly substitute a paradigm using blocks of pictures.
% AD results in
Time series of all subjects were analyzed both in group space and subject space.
For better comparions of subjects, we here report results from the analyses
performed in group space ($z$-maps; Z>3.4, p<.05 cluster-corrected).
% ref to figure
Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary AD
and AV $t$-contrast, and the outline of overlapped, individual PPAs
\citep{sengupta2016extension}.
% MNI space
The $z$-maps and PPA outline are overlayed on the co-registered MNI152 template.
% one slice to show them all
Transversal slice of z=-11 was chosen as it depicts [at least some] voxels of
significant clusters in almost all subjects.
% individual z-maps -> dataset
Results of the analyses that were performed in each subject's subject-space
(unthresholded $z$-maps and thresholded $z$-maps, Z>2.3, p<.05 cluster
corrected) can be found at
\href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.\todo{still
private collection} .
% report here in group

@@

% Sengupta et al., 2016
The visual localizer experiment \citep{sengupta2016extension} yielded bilateral
[parahippocampal] clusters in 12 of 14 subjects and a unilateral right clusters
in two subjects (sub-04, sub-20).
% Sengupta: 1 of 3
Individual PPAs were assessed by visually inspecting thresholded $z$-maps
(Z>1.64, p<.05 cluster corrected) of three different $t$-contrasts
(\textit{strict}, \textit{relaxed}, and \textit{simple} stimulus set, cf.
\citep{sengupta2016extension}).
% Sengupta: procedure a)
Starting with the most conservative contrast (strict set) and a threshold of t =
2.5, we looked for clusters with at least 20 voxels (using AFNI).
%
We titrated [?] the threshold in the range of [2, 3] until we found an isolated
cluster for the PPA.
% Sengupta: procedure b)
If a cluster was not found or not isolated, we used a contrast from the relaxed
set, or finally the simple set, and repeated the process until we found a
cluster that matched the expected anatomical location based on literature
\citep{epstein1998ppa}.

% current analyses: one contrast to localize them all
In the current analyses, we use same contrast of each naturalistic stimulus for
all subjects

for all subjects. We find statistically significant bilateral clusters in nine
subjects, and one cluster in the left hemisphere of sub-09 that are within or
overlapping with the individual PPA.
% subj-04
In sub-04, two homologous clusters are apparent, whereas the dedicated localizer
(and AV stimulus) yielded only one cluster in the right hemisphere.
% AV
Results of the AV contrast yield homologous clusters in five subjects,
unilateral right clusters in six subjects (of which one subjects yielded a
unilateral cluster in the visual localizer), and a unilateral left cluster in
one subject.
% difference to dedicated localizer
We find homologous clusters in sub-20, whereas the dedicated visual localizer
yielded only one cluster in the right hemisphere.
% concluding statement

@@

\subsection{Robustness of PPA across contrasts}

% all eight AV PPA contrasts
Here again in order to test the robustness of our findings, we created four
additional $t$-contrasts for the AV stimulus (see Table \ref{tab:av-contrasts}).
%% results: PPA
All of the overall five AV contrasts yielded significant bilateral clusters that
overlap with the PPA group overlap (see Figure \ref{fig:stability-slices}).
[biggest overlap in posterior part of PPA group overlap  = temporal occipital
fusiform cortex] .
% concluding statement
Here again, we can show that results can in principle be accomplished by varying
the design of the contrasts.
% question
\todo[inline]{concluding statement = interpretation/discussion?}

@@

% all eight AD PPA contrasts
In order to test the robustness of our findings, we created overall eight
$t$-contrasts for the AD stimulus (see Table \ref{tab:ao-contrasts}).
% results
All contrasts except contrast 7 (\texttt{se\_new}, \texttt{se\_old} >
non-spatial categories) and contrast 8 (\texttt{se\_new} > non-spatial
categories) yielded significant bilateral clusters in anterior regions of the
group PPA overlap (see Figure \ref{fig:stability-slices}).
% statement/answer
Results suggest that our findings do not depend on one specific contrasts but
are robust across differently designed contrasts.
% question
\todo[inline]{concluding statement often feels like interpretation/discussion}
%
\todo[inline]{Discussion: discuss that contrasts make ``less and less'' sense}

\todo[inline]{figure caption: mention / explain other clusters}

@@

% precuneus = retrosplenial cortex ?
\todo[inline]{significant clusters in other regions than PPA could or should (?)
also be reported? Following is a short list; depends on the discussion I guess;
anyhow: clusters are not ``random'' but make sense which speaks for the use of
naturalistic stimuli}

>>>>

% intro
Third, we investigated result from both naturalistic paradigms on the level of
individual subjects.
%
Focussing on the AD stimulus, we hypothesize[d] that an exclusively auditory
stimulus can/could localize ``visual area'' in individual subjects and thus
possibly substitute a visual paradigm using blocks of pictures.

@@

% Sengupta et al., 2016
The visual localizer experiment \citep{sengupta2016extension} yielded bilateral
[parahippocampal] clusters in 12 of 14 subjects and an unilateral right clusters
in two subjects (sub-04, sub-20).
% Sengupta: 1 of 3
Individual PPAs were assessed by visually inspecting thresholded $z$-maps
(Z>1.64, p<.05 cluster corrected) of three different $t$-contrasts
(\textit{strict}, \textit{relaxed}, and \textit{simple} stimulus set, cf.
\citep{sengupta2016extension}).
% Sengupta: procedure a)
Starting with the most conservative contrast (strict set) and a threshold of t =
2.5, we looked for clusters with at least 20 voxels (using AFNI).
%
We titrated [?] the threshold in the range of [2, 3] until we found an isolated
cluster for the PPA.
% Sengupta: procedure b)
If a cluster was not found or not isolated, we used a contrast from the relaxed
set, or finally the simple set, and repeated the process until we found a
cluster that matched the expected anatomical location based on literature
\citep{epstein1998ppa}.

% naturalisti stimuli: intro
In the current study, time series of all subjects were analyzed both in subject
space and group space.
% subject space -> NeuroVault
Results of the analyses that were performed in each subject's [subject-]space
(unthresholded $z$-maps and thresholded $z$-maps, Z>2.3, p<.05 cluster
corrected) can be found at
\href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}. \todo{still
private collection}
% here report in group space
For better comparions of subjects, we here report results from the analyses
performed in group space. % ($z$-maps; Z>3.4, p<.05 cluster-corrected).
% one contrast to localize them all; "...and Z>3.4 for all"
Contrary to the procedure in \citep{sengupta2016extension}, we used the same
contrast of each naturalistic stimulus and the same threshold (Z>3.4, p<.05
cluster corrected) for all subjects.

% AV
Results of the primary AV contrast yielded statistically significant bilateral
clusters in five subjects, unilateral right clusters in six subjects (of
which one subjects yielded a unilateral cluster in the visual localizer), and a
unilateral left cluster in one subject.
% difference to dedicated localizer
We find homologous clusters in sub-20, whereas the dedicated visual localizer
yielded only one cluster in the right hemisphere.

% report here in group
Results of the primary AD contrast yielded stastically significant bilateral
clusters in nine subjects, and one cluster in the left hemisphere of sub-09,
that are within or overlapping with the individual PPA.
% subj-04
In sub-04, two homologous clusters are apparent, whereas the dedicated localizer
(and AV stimulus) yielded only one cluster in the right hemisphere.
% ref to figure
Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary AV
and AD $t$-contrast, and the outline of overlapped, individual PPAs
\citep{sengupta2016extension}.
% MNI space
The $z$-maps and PPA outline are overlayed on the co-registered MNI152 template.
% one slice to show them all
Transversal slice of z=-11 was chosen as it depicts [at least some] voxels of
significant clusters in almost all subjects.

@@

\subsection{Robustness of PPA across contrasts: AV \& AD}

@@

% AV
In order to test the robustness of our findings, we created four additional
$t$-contrasts for the AV stimulus (see Table \ref{tab:av-contrasts}) to be
investigated on a group level.
%% results: PPA
All of the overall five AV contrasts yielded significant bilateral clusters that
overlap with the PPA group overlap (see Figure \ref{fig:stability-slices}).
[biggest overlap in posterior part of PPA group overlap  = temporal occipital
fusiform cortex] .
% AD
For the AD stimulus, we created overall eight $t$-contrasts (see Table
\ref{tab:ao-contrasts}).
% results
All contrasts except contrast 7 (\texttt{se\_new}, \texttt{se\_old} >
non-spatial categories) and contrast 8 (\texttt{se\_new} > non-spatial
categories) yielded significant bilateral clusters in anterior regions of the
group PPA overlap (see Figure \ref{fig:stability-slices}).
% statement/answer
Results suggest that our findings do not depend on one specific contrasts but
are robust across differently designed contrasts.\todo{concluding statement
often feels like interpretation}
%
\todo[inline]{figure caption: mention / explain other clusters}

@@

% precuneus = retrosplenial cortex ?
\todo[inline]{Following is a list; report depends on the discussion I guess;
anyway: clusters are not ``random'' but make sense which speaks for the use of
naturalistic stimuli}
